Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb

### 2018-04-05 nb_px_paper/nb_abstract_text.tex
Broke Nb(p,x) paper into container w/ separate body text, appendices, and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

% % ****** Start of file apssamp.tex ******
% %
% %   This file is part of the APS files in the REVTeX 4.1 distribution.
% %   Version 4.1r of REVTeX, August 2010
% %
% %   Copyright (c) 2009, 2010 The American Physical Society.
% %
% %   See the REVTeX 4 README file for restrictions and more information.
% %
% % TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% % as well as the rest of the prerequisites for REVTeX 4.1
% %
% % See the REVTeX 4 README file
% % It also requires running BibTeX. The commands are as follows:
% %
% %  1)  latex apssamp.tex
% %  2)  bibtex apssamp
% %  3)  latex apssamp.tex
% %  4)  latex apssamp.tex
% %
% \documentclass[%
%  reprint,
% superscriptaddress,
% onecolumn,
% linenumbers,
% notitlepage,
% %groupedaddress,
% %unsortedaddress,
% %runinaddress,
% %frontmatterverbose, 
% %preprint,
% %showpacs,preprintnumbers,
% %nofootinbib,
% %nobibnotes,
% %bibnotes,
%  amsmath,amssymb,
%  aps,
% prc,
% %prb,
% %rmp,
% %prstab,
% %prstper,
% %floatfix,
% ]{revtex4-1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Important note on usage                  %%
%% -----------------------                  %%
%% This file must be compiled with PDFLaTeX %%
%% Using standard LaTeX will not work!      %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
% \documentclass[5p]{elsarticle}
% Good for final formatting  - two column
% 
% \documentclass[3p,times]{elsarticle}
% Final formatting
\documentclass[3p]{elsarticle}
% Good for proofing - single column
%

\usepackage[american]{babel}
\usepackage{amsmath}
\usepackage[version=3]{mhchem} 
% \usepackage{fixltx2e}
% \usepackage{refcount}
% \usepackage{siunitx}
% \usepackage{lastpage}
% \usepackage{textcomp}
\usepackage{mathtools}

\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% \usepackage{cool}
% \usepackage{cancel}
\usepackage{microtype}
\usepackage{listings}
\usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% \usepackage{longtable}
\usepackage{subcaption}
\usepackage{booktabs,siunitx}
\usepackage{gensymb}
\usepackage[normalem]{ulem}

% \usepackage{mathtools, cuted}

% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{color}

\usepackage[colorinlistoftodos]{todonotes}

\usepackage[section]{placeins}
\usepackage{multirow}

\usepackage{lineno}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math

\lstset{basicstyle=\small\ttfamily,columns=fullflexible}

% \usepackage{verbatim}

% \usepackage{gensymb}
% \usepackage{enumerate}
% \usepackage{float}
% \usepackage{bm}
% \usepackage{csquotes}
% \usepackage{mathtools}
% \usepackage[sort&compress]{natbib}
% \usepackage{biblatex}

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}

%% The ecrc package defines commands needed for running heads and logos.
%% For running heads, you can set the journal name, the volume, the starting page and the authors

%% set the volume if you know. Otherwise `00'
\volume{00}

%% set the starting page if not 1
\firstpage{1}

%% Give the name of the journal
\journalname{Nuclear Instruments and Methods in Physics Research B}

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{A.S. Voyles et al.}

%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo

%% Give the abbreviation of the Journal.
\jid{nimb}
% \jid{yspmi}

%% Give a short journal name for the dummy logo (if needed)
\jnltitlelogo{Nucl Instrum Meth B}

%% Hereafter the template follows `elsarticle'.
%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.

%% Elsevier CRC generally uses a numbered reference style
%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
%% If using BibTeX, use the style file elsarticle-num.bst

%% End of ecrc-specific commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

\biboptions{sort&compress}

% if you have landscape tables
\usepackage[figuresright]{rotating}

% put your own definitions here:
%   \newcommand{\cZ}{\cal{Z}}
%   \newtheorem{def}{Definition}[section]
%   ...

% add words to TeX's hyphenation exception list
%\hyphenation{author another created financial paper re-commend-ed Post-Script}

% declarations for front matter

\usepackage{fancyvrb}
\usepackage{color}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color
  basicstyle=\footnotesize,        % size of fonts used for the code
  breaklines=true,                 % automatic line breaking only at whitespace
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  keywordstyle=\color{blue},       % keyword style
  stringstyle=\color{mymauve},     % string literal style
}

% Sin and Cos with auto-parentheses 
\newcommand{\sinp}[1]{\sin{\left( #1\right)}}
\newcommand{\cosp}[1]{\cos{\left( #1\right)}}
\newcommand{\expp}[1]{\exp{\left( #1\right)}}
\newcommand{\sinhp}[1]{\sinh{\left( #1\right)}}
\newcommand{\lnp}[1]{\ln{\left( #1\right)}}
\newcommand{\pp}[1]{\left( #1\right)}
\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\norm}[1]{\lVert #1 \rVert}

\newcommand{\textred}[1]{\textcolor{red}{ #1}}
\newcommand{\redactedit}[1]{\textcolor{blue}{ \sout{#1}}}

\newcommand{\cmmnt}[1]{}

\newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}

\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}

\newcommand{\etal}{\emph{et\,al.}}

% Tweak sim for better inline text tilde
\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}

\sisetup{separate-uncertainty=true,table-space-text-post = *}

\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}

% \newcounter{subfigure}[figure]

\newcommand{\subfigimg}[4][,]{%
  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
  \phantom{\usebox1}% Insert appropriate spcing
}
% \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80pt}

\makeatletter
% Make common definition of mean
\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}

\makeatother

\begin{document}

\begin{frontmatter}

%\preprint{APS/123-QED}

% \title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
% % \thanks{A footnote to the article title}%
% 
% \author{Andrew S. Voyles}
%  \email{andrew.voyles@berkeley.edu}
% \affiliation{%
%  Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% }% 
% \author{Lee A. Bernstein}
% \affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
% \affiliation{%
%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% }%
% \author{Eva R. Birnbaum}
% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
% \author{Jonathan W. Engle}
%  \email{jwengle@wisc.edu}
% \affiliation{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
% \author{Stephen A. Graves}
% \affiliation{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
% \author{Toshihiko ??? Kawano}
% \affiliation{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
% %  \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
% \author{Amanda M. Lewis}%
% % \author{Eric F. Matthews}%
% %  \email{Second.Author@institution.edu}
% \affiliation{%
%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% }%
% \author{Francois M. Nortier}
% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory, Los Alamos, NM 87544, USA}

% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
\author[ucb]{Andrew S. Voyles \corref{cor1}}
\ead{andrew.voyles@berkeley.edu}

% \author[lbl]{M.S. Basunia}
% 
% \author[ucb]{J.C. Batchelder}
%

\author[lbl,ucb]{Lee A. Bernstein}

\author[lanl]{Eva R. Birnbaum}

\author[uwm]{Jonathan W. Engle}
\ead{jwengle@wisc.edu}

\author[iowa]{Stephen A. Graves}

\author[tlanl]{Toshihiko  Kawano}

\author[ucb]{Amanda M. Lewis}

\author[lanl]{Francois M. Nortier}

\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
\address[lbl]{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
\address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
\address[lanl]{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
\address[iowa]{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
\address[tlanl]{Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}

% % \collaboration{MUSO Collaboration}%\noaffiliation
% % 
% % \author{Charlie Author}
% % %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
% % \affiliation{
% %  Second institution and/or address\\
% %  This line break forced% with \\
% % }%
% % \affiliation{
% %  Third institution, the second for Charlie Author
% % }%
% % \author{Delta Author}
% % \affiliation{%
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% % }%
% % 
% % \collaboration{CLEO Collaboration}%\noaffiliation
% 
% \date{\today}% It is always \today, today,
%              %  but any date may be explicitly specified
% 
% %% Title, authors and addresses
% 
% %% use the tnoteref command within \title for footnotes;
% %% use the tnotetext command for the associated footnote;
% %% use the fnref command within \author or \address for footnotes;
% %% use the fntext command for the associated footnote;
% %% use the corref command within \author for corresponding author footnotes;
% %% use the cortext command for the associated footnote;
% %% use the ead command for the email address,
% %% and the form \ead[url] for the home page:
% %%
\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}

%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

% \dochead{Short}
%% Use \dochead if there is an article header, e.g. \dochead{Short communication}

% 
% % \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
% \author[ucb]{Andrew S. Voyles \corref{cor1}}
% \ead{andrew.voyles@berkeley.edu}
% 
% % \author[lbl]{M.S. Basunia}
% % 
% % \author[ucb]{J.C. Batchelder}
% 
% 
% \author[ucb,lbl]{Lee A. Bernstein}
% 
% 
% \author[lanl]{Eva R. Birnbaum}
% 
% \author[uwm]{Jonathan W. Engle}
% 
% \author[iowa]{Stephen A. Graves}
% 
% \author[ucb]{Amanda M. Lewis}
% 
% 
% \author[lanl]{Francois M. Nortier}

% \author[ucb]{M.A. Unzueta}
% 
% \author[ucb]{K.A. van Bibber}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

% \cortext[cor1]{Corresponding author}
% \cortext[cor2]{Principal corresponding author}
% \fntext[fn1]{This is the specimen author footnote.}
% \fntext[fn2]{Another author footnote, but a little more longer.}

% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
% \address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
% \address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}

% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
% \address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
% % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
% \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
% \address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
% \address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}

\begin{abstract}

@@

% \begin{description}
% \item[Usage]
% Secondary publications and information retrieval purposes.
% \item[PACS numbers]
% May be entered using the \verb+\pacs{#1}+ command.
% \item[Structure]
% You may use the \texttt{description} environment to structure your abstract;
% use the optional argument of the \verb+\item+ command to give the category of each item. 
% \end{description}
\end{abstract}

% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired

% \begin{abstract}

% \end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Nb+p \sep Cu+p \sep Niobium 
% \sep Copper\sep Aluminum 
\sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep 
% Proton activation \sep 
% Proton transport \sep 
Stacked target activation \sep Monitor reactions \sep 
% Monitor foils 
Medical isotope production \sep Isomer branching ratios \sep  
% Nuclear spin distributions  \sep 
MCNP \sep  LANL
% 
% %% MSC codes here, in the form: \MSC code \sep code
% %% or \MSC[2008] code \sep code (2000 is the default)
% 
\end{keyword}

\end{frontmatter}

% \maketitle

%%
%%  To-do list for comments
%%
% \listoftodos

%%
%% Start line numbering here if you want
%%
\linenumbers

%% main text 
\section{Introduction} \label{sec:intro}

% Referring to abstract:
% % \comment{Stephen:  Not strictly true if you've omitted Na22 and Co56 from your fluence determination.  Update monitors here following discussion.}
% 
% 
% \comment{Comment on the Si production here?  (see red text)}
% 
% \comment{Add extra physics language with Lee.}

% \comment{cite theranostic papers, etc}

Every year, approximately 17 million nuclear medicine procedures (both diagnostic and therapeutic) are performed in the U.S. alone 
% ,  which has made incredible strides in improving our ability to detect and treat a variety of life-threatening diseases 
\cite{Delbeke2011,NSACIsotopesSubcommittee2015}.
% The vast majority
Most of the radionuclides currently used for these procedures are produced 
% in the field's array of
by low- (E \textless\ 30 MeV / A) and intermediate-energy (30 \textless\ E \textless\ 200 MeV / A) accelerators, 
% capabilities, which routinely produce many of the staple medical radionuclides, such as 
e.g., \ce{^{11}C}, \ce{^{18}F}, \ce{^{68}Ga}, \ce{^{82}Rb}, and \ce{^{123}I}. 
These accelerators also produce 
% , as well as many  
% of the 
non-medical radionuclides with commercial value, such as  \ce{^{32}Si}, \ce{^{73}As}, \ce{^{95m}Tc}, and  \ce{^{109}Cd} \cite{international2009iaea,schlyer2008cyclotron}. 
% \comment{Should \enquote{intermediate-energy} be less than 200 MeV, or 100 MeV?  I find conflicting descriptions in the literature.\\Lee:  I believe that 60 MeV is considered as the transition point\\ Stephen: In this context, I would make this definition based on what machines in the US are routinely used for medical isotope production - based on this, I agree with 200 MeV. }
% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}. 
% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.  
Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
% \cite{Qaim201731}. 
% Move next sentence to Fe paper
% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
Candidate isotopes to meet these needs 
% of personalized medicine 
have been identified based on their chemical and radioactive decay properties \cite{NSACIsotopesSubcommittee2015,Qaim201731,bernstein2015nuclear}, and a series of campaigns are underway to perform targeted, high-priority measurements of thin-target cross sections and thick-target integral yields.
These studies will serve to facilitate the production of clinically relevant quantities of radioactivity.

Accurate cross section measurements using  activation methods benefit from well-characterized monitor reactions.  
Currently there is 
% , which  currently
a paucity of such data at intermediate energies, and much of what exists have  high uncertainties (\textgreater15\%).
% One significant obstacle to both high-fidelity measurements of production cross sections for emerging medical radionuclides, as well as conventional isotope production, is a lack of well-characterized  monitor reaction standards.  
% This is particularly true for higher-energy charged particle beams, where there is currently a paucity of such data. 
% Lee - cut?
Indeed, the development of new monitor reaction standards and the improved evaluation of existing standards is one of the areas of greatest cross-cutting need for nuclear data \cite{bernstein2015nuclear}. 
% Charged particle monitor reaction data currently exists for several low-to-intermediate energy charged particle beams (E \textless\ 50 MeV / A), but even the experimental data used for this evaluation are  sparse above approximately 30 MeV / A and  uncertainties in experimental cross sections are large (6--15\%) \cite{gul2001charged}. 
% While work is needed to improve upon existing monitor reaction data, the development of n
% Lee - cut?
New reactions can expand the available range of options for the monitoring of charged particle beams.
This work 
% in particular seeks to improve this range of options by 
is an attempt to characterize a new monitor reaction for  proton beams in excess of 40 MeV, for possible use at isotope production facilities such as the  Brookhaven Linac Isotope Producer (BLIP) at Brookhaven National Laboratory, 
% IPF
the Isotope Production Facility (IPF) at  Los Alamos National Laboratory, or the Separated Sector Cyclotron at the 
% iThemba LABS
iThemba Laboratory for Accelerator Based Sciences.
% \comment{Stephen: I'm having a hard time following this paragraph. Some of your syntax overlaps significantly with nuclear medicine \& medical physics terminology with different intended meanings. For example 'dosimetry' is typically taken to mean the measurement of absorbed energy per unit mass (J/kg) and associated measurements/specifications. Another example, 'dosimetry standard' is used quite often when referring to NIST air kerma reference standards which are the bedrock of Accredited Dosimetry Calibration Lab (ADCL) measurements. As you are more familiar with classic Nuclear Physics writing, perhaps you better know how this language will be interpreted. }

% % 
% 
% Most of this should be more appropriate for the PhD thesis?
% 
% % 
% Activation analysis is one of the most fundamental measurement techniques in experimental nuclear physics, as it is a simple and straightforward method to probe the structure and behavior of nuclear matter,  dating back to the infancy of the field \cite{ehmann1993radiochemistry,krüger1971principles}. 
% % All activation measurements involve the analysis and quantification of decaying radioactive nuclei created through irradiation via ionizing radiation \cite{ehmann1993radiochemistry,krüger1971principles}.
% % \comment{Lee:  I think that you might want to mention a connection to BLIP, IPF, iThemba etc. here, and make it clear that you're dealing with protons only, not neutrons.  }
% Monitor reactions have  historically been part of such activation experiments, and serve two valuable purposes for charged particle-induced reactions, depending upon the energy regime.  
% % \comment{Stephen:  Move much of the remaining intro section into the Discussion, for brevity?}
% Between the reaction's energetic threshold  and the end of its compound peak, the magnitude and shape of the excitation function changes rapidly with increasing energy, making it useful for determining the energy distribution of particles which have traversed a thin irradiated target.
% This is particularly the case when comparing  monitor reactions leading to two distinct residual nuclei from the same target, such as the $^\text{nat}$Cu(p,x)\ce{^{62}Zn} and $^\text{nat}$Cu(p,x)\ce{^{63}Zn} reactions \cite{gul2001charged}.
% This is extremely valuable, as it allows the screening and minimization of systematic errors based on energy determination, though this energy sensitivity  precludes their reliability as a beam current monitor.  
% In the higher energy  of the reaction's pre-equilibrium tail, the excitation function becomes  smooth and generally flat as a function of energy.
% This  offers little-to-no energy sensitivity, but  is extremely useful for determining the integral beam current. 
% While cross section measurements often use external beam current monitors (such as an inductive pickup upstream of a target, or an electrically-isolated target in a Faraday cup), these measure the integrated current incident upon the \enquote{front} (upstream) of the target assembly.
% % For the case of stacked-target activation experiments, commonly employed to measure cross sections at multiple energies  in a single activation, external beam current monitors can only measure the integral current incident upon the \enquote{front} (upstream) of the target stack.
% % In these experiments, a
% A series of monitor foils at each energy position allows one to indirectly measure the integral current at each position within the stack, reducing systematic errors in observed cross section magnitude, but with reduced precision compared to direct measurement using a well-characterized suppressed Faraday cup.
% % \comment{Stephen:  ``and precision, unfortunately ''.  Update post-discussion.}
% Both of these purposes make well-characterized monitor reactions an invaluable asset to any activation experiment.

% In theory, nearly any radioisotope can serve as a reaction monitor, but 
% those desired to be classified as a 
Desirable monitor reactions 
% standard 
possess several hallmark characteristics,  
% The primary factor involved in selecting a new monitor is ensuring that the desired radionuclide emit  at least one (preferably multiple, to ensure accurate radionuclide identification) distinct decay gamma-rays which can be used to uniquely identify it during post-activation assay.  
% Primarily, this means selecting a radionuclide product with 
% a number of 
including intense and distinct gamma-rays, 
% with high intensities,  
which can be used to uniquely identify it during post-activation assay, and lifetimes long enough to enable removal after a reasonable length irradiation.    
% The decay radiation should preferably have high intensities, so that they show up as strong peaks, and minimize the amount of time needed to count the activated target in order to achieve acceptable counting statistics. 
% \comment{Stephen:  These next 2 paragraphs are better suited for the discussion, specifically addressing how this problem affects your particular experiment. }
Care should also be taken to avoid cases where two radionuclides which are produced by two different reactions on the same monitor foil lead to states in the same daughter nuclide.  
For example, \ce{^{48}V}  ($t_{1/2}$ = 15.97 d, $\epsilon=100\%$ to \ce{^{48}Ti}) and \ce{^{48}Sc}  ($t_{1/2}$ = 43.67 h, $\beta^-=100\%$ to \ce{^{48}Ti}) can both be formed via $^\text{nat}$Ti(p,x) reactions, yielding the same 983.52 keV transition in \ce{^{48}Ti} \cite{Burrows2006}.
% Fortunately, these cases can occasionally be mitigated by either using a difference in half-life between the two feeding pathways to allow one to decay out, or by using a distinct gamma-ray from one of the two isobar nuclei to subtract out the activity associated with it (such as the $E_\gamma=1037.522$ keV, $I_\gamma=97.6\%$ line in the decay of \ce{^{48}Ti}) \cite{Burrows2006}.
% However, this approach propagates larger uncertainties into the final activity of the desired monitor nucleus, so in principle it is far preferred to choose a monitor reaction which does not have overlapping gamma-rays from another isobar nucleus.
% Another important decay factor to consider is that of the half-life of the desired monitor nucleus.
% Ideally, the nucleus has a lifetime which is comparable to that of the reaction products being studied, and sufficiently long-lived to ensure that it may be quantified  conveniently 
% and leisurely 
% following end-of-bombardment.
% without the majority if it decaying away.
% In addition, it is preferred that the lifetime be comparable to that of the reaction products being studied. 
% For proper quantification, i
It is also of vital importance that the proposed monitor nucleus have well-characterized decay data.
This includes a precise and well-established half-life,  
% needed to  correct for decay losses, 
as well as well-characterized decay gamma-ray intensities.
% In practice, the weakest components of decay data are often the gamma-ray intensities, which can routinely have uncertainties of 5\% or more.
% Since this uncertainty is propagated in quadrature from the activity of both the monitor reaction and the reaction product being studied, choosing a monitor with a well-established gamma-ray intensity can make a significant reduction in measured cross section uncertainties.
From a targetry  perspective, it is preferable to use a naturally mono-isotopic target that is readily available
% readily commercially available at an affordable price and is 
and  chemically inert.
% --- any significant chemical changes during target preparation (significant oxidation, etc.) will affect the target's areal density, systematically changing the measured integral current. 
% Structurally, the target material should be malleable and supportive to be able to be formed into a thin target.
% For charged particle reactions,  energy degradation scales with target areal density,  broadening the energy spectrum downstream of the target.
% However, since the monitor reaction yield also scales with target areal density, the use of a target which is too thin may provide insufficient counting statistics during decay spectrometry.
% For reference, a monitor foil of approximately 25 mg/cm$^2$ provides a good compromise, with less than 100 keV degradation for a proton energy of 100 MeV, and less than 200 keV at 40 MeV.
Targets which can be formed into a wide thickness range are convenient, as selection is subject to the context of an experiment, seeking to maximize thickness without overly perturbing the energy uncertainty of  measurements.
% These are the primary characteristics involved in choosing an appropriate target for a monitor reaction
% \comment{Stephen:  This is also a discussion point. If you're trying to introduce the purpose of this paper, i.e. the establishment of a new monitor reaction, I would try to condense paragraphs 3--9 into two paragraphs: one paragraph explaining what a monitor reaction is used for, and the other describing considerations relevant to the use of a monitor reaction. The rest of this content can be included in the discussion if you feel it is necessary.}
Lastly, and perhaps most importantly for high-energy monitor reaction applications, it is  of utmost importance to choose a reaction channel which cannot be populated via secondary particles incident upon the monitor target.
Typically, this is  mostly a concern for secondary neutrons produced through (z,xn) reactions, 
% on upstream targets, degraders, and stack materials, to avoid monitor reactions which can be populated through (n,x) reactions on the target.
% Any
but any monitor reaction channel which can be populated by anything other than the primary beam should be avoided, as it is often 
% a laborious task 
difficult to accurately and unambiguously separate out the fraction of secondary particles contributing to the total activation.

One  reaction which satisfies these requirements is that of a new, intermediate-energy proton monitor reaction standard based on \ce{^{93}Nb}(p,4n)\ce{^{90}Mo}. 
Niobium is naturally mono-isotopic, readily  available commercially in high purity, is fairly chemically inert, and can easily be rolled down to foils as thin as 1 $\micro$m.  
\ce{^{90}Mo} also has 
% excellent decay properties ---
a sufficiently long lifetime ($\epsilon=100\%, t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997})  
% allows it to be counted at leisure without fear of the product \ce{^{90}Mo} decaying away excessively between end-of-bombardment and the start of counting, and it possesses
and seven strong, distinct gamma lines (notably its 122.370 keV [$I_\gamma = 64 \pm 3\%$] and 257.34 keV [$I_\gamma = 78 \pm 4\%$] lines) which can be used to uniquely and easily   quantify \ce{^{90}Mo} production. 
In addition,  \ce{^{90}Mo} is completely immune from (n,x) production on  \ce{^{93}Nb}, being produced only via the primary proton beam, and the \ce{^{90}Mo} decay lines can only be observed in its decay, as its daughter, \ce{^{90}Nb}, is also unstable and decays via $\epsilon$ to stable \ce{^{90}Zr}.

The purpose of the present work is to  measure the production of the long-lived radionuclide \ce{^{90}Mo}  
% ($t_{1/2}=5.56 \pm 0.09$ h \cite{Browne1997}) 
via the $^\text{nat}$Nb(p,x) reaction. 
In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of 37 other (p,x) production cross sections between 40--90 MeV  for a number of additional reaction products, including several emerging radionuclides with medical applications.
% These include the non-standard positron emission tomography (PET) agents \ce{^{57}Ni}  ($t_{1/2}=35.60\pm0.06$ h \cite{Bhat1998}), \ce{^{64}Cu} ($t_{1/2}=12.701 \pm 0.002$ h \cite{Singh2007}), \ce{^{86}Y}  ($t_{1/2}=14.74\pm0.02$ h \cite{NEGRET20151}), \ce{^{89}Zr} ($t_{1/2}=78.41\pm0.12$ h \cite{Singh2013}),  \ce{^{90}Nb} ($t_{1/2}=14.60 \pm 0.05$ h \cite{Browne1997}),  and the diagnostic agent \ce{^{82\text{m}}Rb} ($t_{1/2}=6.472\pm0.006$ h \cite{Tuli2003}). 
These include the non-standard positron emitters \ce{^{57}Ni}, \ce{^{64}Cu},  \ce{^{86}Y}, \ce{^{89}Zr},  \ce{^{90}Nb}, 
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
and the diagnostic agent \ce{^{82\text{m}}Rb}.

%   \comment{The following paragraph should only be included if we decide to touch on spin physics in this manuscript, or split it into a follow-on PhysRev C, etc.}
%   
%   \comment{Stephen:  If included in this paper, I would move to the discussion. It's not clear yet in the paper that you have the data required to make these determinations.}

>>>>

@@

% \begin{description}
% \item[Usage]
% Secondary publications and information retrieval purposes.
% \item[PACS numbers]
% May be entered using the \verb+\pacs{#1}+ command.
% \item[Structure]
% You may use the \texttt{description} environment to structure your abstract;
% use the optional argument of the \verb+\item+ command to give the category of each item. 
% \end{description}
